\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-02-01 doc/USER_MANUAL/06_fault_sources.tex
Modify fault solver part of the manual.

During mesh generation, the fault is defined by two surfaces in contact.
Let's denote as \textquotedbl{}\emph{side 1}\textquotedbl{} the SECOND
surface declared by the user in the call to the python function \textquotedbl{}\emph{fault\_input}\textquotedbl{},
and the FIRST surface as \textquotedbl{}\emph{side 2}\textquotedbl{}.
The local coordinate system on the fault is defined as the right-handed
coordinate system defined by (strike, dip, normal), where \textquotedbl{}\emph{normal}\textquotedbl{}
is the normal vector outgoing from side 1, \textquotedbl{}\emph{dip}\textquotedbl{}
is parallel to the along-dip direction pointing downwards, and \textquotedbl{}\emph{strike}\textquotedbl{}
is the horizontal along-strike vector such that the system is right-handed.\\

>>>>

During mesh generation, the fault is defined by two surfaces in contact.
Let's denote as \textquotedbl{}\emph{side 1}\textquotedbl{} the SECOND
surface declared by the user in the call to the python function \textquotedbl{}\emph{fault\_input}\textquotedbl{},
and the FIRST surface as \textquotedbl{}\emph{side 2}\textquotedbl{}.
The local coordinate system on the fault is defined as the right-handed
coordinate system defined by (strike, dip, normal), where \textquotedbl{}\emph{normal}\textquotedbl{}
is the normal vector outgoing from side 1, \textquotedbl{}\emph{dip}\textquotedbl{}
is parallel to the along-dip direction pointing downwards, and \textquotedbl{}\emph{strike}\textquotedbl{}
is the horizontal along-strike vector such that the system is right-handed. In places where the fault plane is horizontal,
we define the alone strike direction to be (1,0,0).\\
